\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.2cm, top=0.4cm, right=1.0cm, bottom=0.5cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{0.5mm}}

\begin{document}

% Header
\begin{center}
    {\Huge\textbf{Amit Kumar Yadav}} \\
    \vspace{1mm}
    \small{\textbf{Backend Engineer} $|$ Go, Rust, Blockchain \& Distributed Systems $|$ (+91) 7017885121 $|$ \href{mailto:amitkumaryadav191@gmail.com}{amitkumaryadav191@gmail.com} $|$ \href{https://amit22-yadav.github.io/Amit-yadav-portfolio/}{Portfolio} $|$ \href{https://www.linkedin.com/in/amit-kumar-yadav-44260419b/}{LinkedIn} $|$ \href{https://github.com/Amit22-yadav}{Github} $|$ \href{https://substrate.stackexchange.com/users/2281/amit-kumar-yadav}{StackExchange}}
\end{center}
\vspace{-7mm}

\section*{Summary}

\small{
Backend engineer with 4+ years of production experience in Go, Rust, blockchain protocol engineering, and distributed systems. Shipped consensus-level work on a PolyBFT EVM L1 (Hydragon) in Go — slashing module, EVM hard-fork upgrade, and IBFT quorum fixes. Authored a Substrate/FRAME pallet in Rust, integrated Frontier (EVM) into two Substrate chains, and delivered 5 production Sui Move contracts. Currently building a Rust order-matching engine sustaining 728K orders/sec.
}

\section*{Professional Experience: Antier Solutions (February 2022- Present)}

\vspace{-0.4mm}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Order Matching Engine (Centralized Exchange)}{Mohali, India}
      {Rust Backend Engineer}{March 2026 - Present}
      \resumeItemListStart
        \resumeItem{Engine Core: }{High-throughput Rust matching engine supporting limit and market orders with a price-time priority order book; sustaining 728K orders/sec and peaking above 1M orders/sec under burst load on commodity hardware.}\newline
        \textbf{Tech}: Rust, Tokio, async/await, criterion benchmarks.
      \resumeItemListEnd


  \resumeSubheading
      {Hydra Chain (Hydragon Node)}{Mohali, India}
      {Protocol Engineer}{February 2025 - December 2025}
      \resumeItemListStart
        \resumeItem{Consensus Engineering: }{Built a validator slashing module for PolyBFT with double-sign detection and on-chain slashing-contract submission across 5 merged PRs; also fixed a quorum-calculation bug in HasQuorum that caused 100\% block stalls for validator sets under 4 nodes.}
        \resumeItem{EVM Hard-Fork Upgrade: }{Upgraded Hydragon EVM across 2 hard forks (London $\rightarrow$ Paris $\rightarrow$ Shanghai) by implementing 4 EIPs (4399, 3855, 3860, 3651), and contributed to the on-chain Solidity slashing contracts wired to consensus-layer system transactions.}
        \resumeItem{P2P / Networking: }{Reworked peer persistence and multi-source bootnode discovery across 3 PRs, eliminating stale-peer reconnect storms after restart and reducing post-restart reconnect latency.}\newline
        \textbf{Tech}: Go, EVM internals, PolyBFT, Geth, libp2p, Solidity. \textbf{Links}: \href{https://github.com/Hydra-Chain/hydragon-node/pull/122}{Slashing PR}, \href{https://github.com/Hydra-Chain/hydragon-node/pull/123}{EVM Upgrade PR}, \href{https://github.com/Hydra-Chain/hydragon-node/pulls?q=is\%3Apr+author\%3As-h-ubham+is\%3Aclosed}{Merged PRs}.
      \resumeItemListEnd


  \resumeSubheading
      {HYDRO}{Mohali, India}
      {Smart Contract Developer (Sui Move)}{February 2024 - January 2025}
      \resumeItemListStart
        \resumeItem{Smart Contracts: }{Designed and shipped 5 production Sui Move contracts to mainnet — Token, Migration, Vesting, Staking, and Rewards Distribution — forming the on-chain backbone of the HYDRO token economy over 12 months.}\newline
        \textbf{Tech}: Sui Move, Sui CLI, Bitbucket. \textbf{Links}: \href{https://suiscan.xyz/mainnet/object/0x4bb07b086c13bda7af26b9872fa8c4b460a9c0479cde6a63de4b9d29ea0ec99a/contracts}{Token}, \href{https://suiscan.xyz/mainnet/object/0xbfa32851690179e9576df04d932108040ca585f5c9ee487908b5ae92466367a8/contracts}{Migration}, \href{https://suiscan.xyz/mainnet/object/0xcee7a9493802ad54cd28411c69158cb21d7fb945b39d608a1cf989670d8ed4b0/contracts}{Vesting}, \href{https://suiscan.xyz/mainnet/object/0x123fc385b4d17d0cfe9d9f561dd475b163db6f91fbb7481af5019fe3032baa6c/contracts}{Staking}, \href{https://suiscan.xyz/mainnet/object/0x9ab7bdf99a40beb91835b6d948d13ffef96b1c10cc2b026b03512fdad3b46ebc/contracts}{Rewards}.
      \resumeItemListEnd


  \resumeSubheading
      {5ireChain}{Mohali, India}
      {Core Blockchain Developer}{December 2022 - July 2023}
      \resumeItemListStart
        \resumeItem{EVM Integration: }{Integrated \href{https://github.com/paritytech/frontier}{Frontier (EVM)} into \href{https://github.com/5ire-tech/5ireChain}{5ireChain} over 8 months, delivering an EVM + WASM dual-VM L1 supporting 100\% Ethereum-tooling compatibility.}
        \resumeItem{ESG Pallet: }{Authored the \href{https://github.com/5ire-tech/5ireChain/tree/master/frame/esg}{ESG pallet} in Substrate/FRAME — a validator-scoring module that adjusts block rewards based on Sustainability Score; validated end-to-end on a local multi-validator testnet. (\href{https://explorer.5ire.network}{Explorer})}
      \resumeItemListEnd


  \resumeSubheading
      {Earlier Roles at Antier Solutions}{Mohali, India}
      {Blockchain Developer}{June 2022 - January 2024}
      \resumeItemListStart
        \resumeItem{CTRL ALT (Nov 2023 - Jan 2024): }{Designed and shipped an Algorand on-chain voting contract using PyTeal + Beaker over a 3-month engagement, containerized via Docker for reproducible deployments.}
        \resumeItem{SaitaChain (Aug 2023 - Oct 2023): }{Implemented NPOS consensus pallets and Frontier (EVM) compatibility on a Substrate-based EVM and WASM L1 within a 3-month delivery window.}
        \resumeItem{Peer / VINE Chain (Jun 2022 - Dec 2022): }{Bootstrapped a Substrate L1 from scratch over 6 months — chain spec, genesis config, NPOS validator set, and forkless runtime upgrades. (\href{https://vne.network}{Network}, \href{https://validator.vne.network}{Validator}, \href{https://nominator.vne.network}{Nominator})}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

% \section*{Skills}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
\section{Technologies}

\small{
\textbf{Languages:} Rust, Go, Solidity, Sui Move, Python, PyTeal, C++, SQL. \\
\textbf{Blockchain:} Substrate, FRAME, Frontier (EVM), PolyBFT, EVM internals (EIPs, opcodes, gas metering), Sui, Algorand, Cosmos SDK, Beaker, libp2p. \\
\textbf{Smart Contracts:} ERC-20, Staking, Vesting, Governance / Voting, Token Migration, Rewards Distribution, Slashing. \\
\textbf{Backend / Systems:} Tokio, async Rust, criterion benchmarking, REST APIs, Docker. \\
\textbf{Cloud \& Databases:} AWS (Lambda, AppSync, S3, SNS), PostgreSQL, DynamoDB. \\
\textbf{Developer Tools:} Git, GitHub, GitLab, Bitbucket, Jira, VS Code. \\
\textbf{Operating Systems:} Linux, macOS, Windows.
}

\section{Education}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\item {Babu Banarasi Das University, Lucknow, UP.} { Master’s of Computer Applications (MCA) (CGPA: 8.2/10)}.\newline {June 2018 -- June 2020}
\item {HNB Garhwal University, Srinagar, UK.} {Bachelor's of Computer Applications(BCA) (CGPA: 6.5/10 )}.\newline {June 2015 -- June 2018}
\resumeSubHeadingListEnd



% \section*{Languages}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumeItem{English, Hindi, Punjabi}{}
% \resumeSubHeadingListEnd

% \section*{Hobbies}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumeItem{Trekking, Traveling, Dancing, Shopping}{}
% \resumeSubHeadingListEnd


        
\end{document}
